Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
n not N

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks,
ranging from directly observed to remotely sensed [@Davis_2018; @Webber_2019].
Remotely sensed GPS data is commonly collected at a fixed rate, e.g. every $x$
minutes or hours, continuously throughout the study period. Fix rate is a
reflection of number of observations an individual would have been observed and
recorded in traditional ethological studies. To investigate the influence of
number of observations, we generated multilayer networks of social association
between `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers
(foraging, forest, and open) using $N$ randomly selected observations. We first
generated a maximum of 1000 timesteps and iteratively used $N$ of these ($N$ =
10 - 1000 observations by steps of 10), to ensure previously included timesteps,
and resulting associations, were accumulated with subsequent observations to
mimic collection of observational data. Within each multilayer network with $N$
observations, we calculated individual graph strength and multidegree. We
calculated edge overlap across the entire series of networks to determine
proportion of total edges as number of observations increased.

>>>>

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks,
ranging from directly observed to remotely sensed [@Davis_2018; @Webber_2019].
Remotely sensed GPS data is commonly collected at a fixed rate, e.g. every $x$
minutes or hours, continuously throughout the study period. Fix rate is a
reflection of number of observations an individual would have been observed and
recorded in traditional ethological studies. To investigate the influence of
number of observations, we generated multilayer networks of social association
between `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers
(foraging, forest, and open) using $n$ randomly selected observations. We first
generated a maximum of 1000 timesteps and iteratively used $n$ of these ($n$ =
10 - 1000 observations by steps of 10), to ensure previously included timesteps,
and resulting associations, were accumulated with subsequent observations to
mimic collection of observational data. Within each multilayer network with $n$
observations, we calculated individual graph strength and multidegree. We
calculated edge overlap across the entire series of networks to determine
proportion of total edges as number of observations increased.
